\section*{\color{Maroon}Work Experience}
\hrule \smallskip
\noindent
\begin{flushright}
\begin{tabular}{r|l}
\indent March 2016 - \textit{Present} & \textbf{Consultant} \\
\indent & {\large{QA Consulting, Manchester}} \\
\end{tabular}
\end{flushright}
\begin{itemize}
\item
	\indent \textit{Software Engineer} \newline
	\indent \textbf{\underline{HM Revenue \& Customs}} \newline 
	\indent {Took part in a team to develop a new content management system for fraud prevention which interacts with different project endpoints, irrespective of repository. This was comprised of several different REST microservices within Spring Boot which made for a composite system to ingest, retrieve and search content. This was built using test driven development and adhered to an industry production standard.} \newline \newline
    Main contribution to the project was creating a custom deserialiser using the Jackson API and integrating Spring Sleuth into the existing customised logger using Log4J, later replacing it with Logback. Also responsible for bug-fixing and implementing an exception mapper to catch specific exceptions relevant to the project.
    On rotation I was a Java tester. I made use of jUnit as the main basis for testing Java code, Cucumber (Gherkin) to create the feature files, Selenium for automated testing of UI elements, Mockito to mock behaviours when reliant on other files and 	Rest-Assured for automated testing of REST services. This made use of behavior driven development and end-to-end testing of services, as opposed to software developments test driven development which test individual code segments.
   	Also exercised skills in Jenkins creating jobs to build or deploy projects.\newline \newline
   	All work was conducted in an agile scrum environment which consisted of a series of eight 2 week sprints. These included joining in sprint planning to form stories, input ability to complete work committed to and forming the next 2 week sprint periods, daily stand-ups where daily progress is shared with the team \& sprint reviews and retrospectives which looked at the work completed and how the next sprint could be achieved better.\newline
\item
	\indent \textit{Platform Engineer} \newline
	\indent \textbf{\underline{Capgemini}} \newline 
	Contracted to Capgemini for research \& development of a cloud based platform using tools such as the Amazon web services EC2 and Hashicorps Vagrant and Terraform to provision environments for use in the context of API provisioning, identity 			management, automated provisioning and service management.\newline \newline          
	Strong  use  of  UNIX  based  operating  systems  as well as OS X. Worked within an agile scrum environment. My contributions include  implementing  an  automated  service  desk, researching  advanced  security  software  such  as OSSec \& SELinux as well as provisioning environments for pre-release clients.
	\smallskip 
	\noindent 
\end{itemize}

\begin{flushright}
\begin{tabular}{r|l}
\indent January 2015 - April 2015 & \textbf{Teaching Assistant} \\
\indent & {\large{Brampton Manor Academy}} \\
\indent & East Ham
\end{tabular}
\end{flushright}

\noindent Assigned a 10 week placement for a university module working with a year 8 class. Duties included assisting the teacher in aiding learning to pupils and answering any technical questions students have relating towards curriculum and beyond. Given control of the classroom for 20 minutes each week to teach material derived from own lesson plan with highly positive feedback and thorough enjoyment from all students. Demonstrated excellent aptitude for teaching. \newline